---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Loading data

We're gonna look at Instacart data.

```{r, message=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)

data("instacart")
```


# Plotly plots

## Scatterplot

This plot shows the number of items ordered in each department, lowest to highest.

```{r, warning=FALSE}
instacart %>% 
  count(department) %>% 
  mutate(
    department = factor(department),
    department = fct_reorder(department, n)
  ) %>% 
  plot_ly(
    x = ~department, y = ~n,  
    alpha = .5, type = "scatter", mode = "markers")
```

## Bar plot

This plot shows the number of items ordered in beverage and snacks aisle, lowest to highest under each department.

```{r}
aisle_df =
instacart %>%
  group_by(department) %>% 
  count(aisle) %>% 
  filter(department == "beverages" | department == "snacks") %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)  
  ) 

aisle_df %>% 
  mutate(text_label = str_c("Department: ", department)) %>% 
  plot_ly(
    x = ~aisle, y = ~n, color = ~department, text = ~text_label, 
    alpha = .5, type = "bar", colors = "viridis") 
```

## Line plot

This plot shows the number of orders placed in each hour of the day on weekends (Friday, Saturday, Sunday).

```{r}
dow_df = 
  instacart %>% 
  mutate(order_dow = factor(order_dow)) %>% 
  filter(order_dow == '5' | order_dow == '6' | order_dow == '0') %>% 
  group_by(order_dow, order_hour_of_day) %>% 
  count(order_hour_of_day) 

dow_df %>% 
  ungroup() %>% 
  plot_ly(
    x = ~order_hour_of_day, y = ~n, color = ~order_dow,
    type = "scatter", mode = "lines+markers", colors = "viridis")
 
```

